---
title: "Using the metameta package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the metameta package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 3
)
```



The metameta package includes a set of functions to re-analyse published meta-analyses. Let's begin by calculating the statistical power of each study included in a meta-analysis. This function will calulate power assuming that the reported summary effect size estimate is the true effect sizes (the "observed_es" argument) as well as assuming a range of possible true effect sizes, ranging from 0.1 to 1 (in increments of 0.1).

This particular meta-analysis includes 9 studies, and reported both the effect size and standard error in a forest plot (for more information on this study, see the documentation page: `?dat_ooi`). Here, we're only showing the first 6 columns for the purposes of illustration, although the function calculates power for 11 true effect sizes in total.

```{r, message=FALSE}
library(metameta)
library(dplyr)

power_ooi <- mapower_se(dat = dat_ooi, observed_es = 0.178, name = "ooi et al 2017")
power_ooi_dat <- power_ooi$dat
power_ooi_dat <- power_ooi_dat %>% select(1:6) # Select first 6 columns
power_ooi_dat
```

There's also a similar function for calculating the statisical power of a meta-analysis that reports effect size and _confidence interval data_, which is often reported if standard error data isn't reported. As before, we're only printing a selection of columns.

```{r, message=FALSE}
library(metameta)
library(dplyr)

power_keech <- mapower_ul(dat = dat_keech, observed_es = 0.08, name = "Keech et al 2017")
power_keech_dat <- power_keech$dat
power_keech_dat <- power_keech_dat %>% select(1:6) # Select first 6 columns
power_keech_dat
```

Sometimes it's useful to calculate the statistical power for a body of meta-analyses, which might be reported in the same article or accross articles. Illustrating the power of individual studies from multiple meta-analyses can be difficult to interpret if there are many studies. An alternative is to illustrate the power per meta-analysis by calculating the mean power accross studies. We can illustrate this with a "Firepower" plot.

Before we create our Firepower plot, we need to prepare the datafile

```{r, message=FALSE}
### Calcuate median power for three meta-analyses
power_ooi <- mapower_se(dat = dat_ooi, observed_es = 0.178, name = "ooi et al 2017")
power_med_ooi <- power_ooi$power_median_dat

keech_power <- mapower_ul(dat = dat_keech, observed_es = 0.08, name = "Keech et al 2017")
power_med_keech <- keech_power$power_median_dat

power_bakermans_kranenburg <- 
  mapower_se(dat = dat_bakermans_kranenburg, observed_es = 0.32, 
             name = "Bakermans-Kranenburg et al 2013")
power_med_bakermans_kranenburg <- power_bakermans_kranenburg$power_median_dat

### Create a list
list_power <- list(power_med_ooi, power_med_keech, power_med_bakermans_kranenburg)
```

Now, we can create our plot using the list we created.

```{r, message=FALSE}
### Run firepower function
fp <- firepower(list_power)

### Create firepower plot
fp_plot <- fp$fp_plot
fp_plot
```

You can also print and store the data underlying this figure. 

```{r, message=FALSE}
fp_data <- fp$dat
fp_data
```
